% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{fontawesome}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black 
    %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
                & +91-80872 99526\\
	\textbf{\href{https://ms-choudhary.github.io/}{\LARGE Mohit Choudhary}} & \href{mailto:msch0udhary@protonmail.com}{msch0udhary@protonmail.com}\\
	{Bangalore, India} & \href{https://ms-choudhary.github.io}{https://ms-choudhary.github.io} \\
                & \faGithub \href{https://github.com/ms-choudhary}{/ms-choudhary} \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
	\begin{description}[noitemsep]
		\item[Languages:] { \footnotesize Go, Elixir, Ruby, Bash}
		\item[Databases:] { \footnotesize Etcd, PostgreSQL, Elasticsearch, Redis}
    \item[CI/CD:] { \footnotesize Gitlab, Gitlab CI}
    \item[Cloud Providers:] { \footnotesize AWS }
    \item[Container Orchestration:] { \footnotesize Kubernetes }
    \item[Tools:] { \footnotesize Ansible, Packer, Terraform, Vagrant, Docker }
    \item[Logging/Monitoring:] { \footnotesize Prometheus, Grafana, Loki, Graylog }
    \item[OS:] { \footnotesize Linux, Unix, QEMU }
	\end{description} % End Skills list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.svnit.ac.in/}{National Institute of Technology - Surat}}{Surat}{{Bachelor of Technology in Computer Engineering}; {CGPA:7.87/10.00}}{Jun. 2010 -- Jun. 2014}
				{ \footnotesize
				\begin{itemize}
					%\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
					\resitem{Key Courses: Computer Architecture, Computer Networks, Operating System, Digital Circuits, Compilers, Algorithms, Data Structures, C}
					\resitem{\textbf{{Projects:}}} 
						\begin{itemize}
							\resitem{HPC implementation in Cloud Computing - Researched various possibilities of parallel computing}
							\resitem{Malware detection in Android based platforms - Based on clustering of linux system calls}
						\end{itemize}
				\end{itemize}
				}
	\end{itemize} % End Education list


%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{itemize}
		\item 
			\ressubheading{\href{https://scripbox.com/}{Scripbox}}{Bangalore}
				{Lead Devops Engineer}{Jul. 2017 -- Present}
				{ \footnotesize
				\begin{itemize}
					\resitem{Developed and responsible for maintaining highly available centralized authentication service, which uses JWT tokens for authentication}
					\resitem{Maintaining highly active internal communication service that sends monthly newsletters as well as event based communication}
					\resitem{Custom auto-scaling of applications on Kubernetes based on application metrics}
					\resitem{Responsible for maintaining two Kubernetes cluster (staging \& production) on AWS}
					\resitem{Responsible for triaging \& resolving production incidents}
				\end{itemize}
				}
\begin{comment}
      \ressubsubheading{Product Engineer}{Aug. 2019 -- Present}
        { \footnotesize
        \begin{itemize}
          \resitem{Maintiaining Sanchaar}
          \resitem{blah}
          \resitem{blah}
        \end{itemize}
        }
\end{comment}


		\item 
			\ressubheading{\href{https://www.amdocs.com/}{Amdocs}}{Pune}{Software Developer}{Jan. 2016 -- Jun. 2017}
				{ \footnotesize
				\begin{itemize}
					\resitem{Developed web service to generate reports of captured orders for specific products}
					\resitem{Developed web service to capture orders in OCX (Ordering Capture Express)}
				\end{itemize}
				}
      \ressubsubheading{Software Developer Associate}{Jun. 2014 -- Jan. 2016}
        { \footnotesize
        \begin{itemize}
          \resitem{Worked on core team which develops generalized Ordering framework}
        \end{itemize}
        }
	\end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%

\resheading{Certifications}
  \begin{itemize}
      \resitem{\footnotesize \href{https://ti-user-certificates.s3.amazonaws.com/e0df7fbf-a057-42af-8a1f-590912be5460/51db2b03-30f4-54b3-9cbb-456782c62bd8-mohit-s-choudhary-certified-kubernetes-administrator-cka-certificate.pdf}{Certified Kubernetes Administrator (CKA)}}
  \end{itemize}

\resheading{Projects}

\begin{description}
  \item[{\href{https://github.com/ms-choudhary/cachr}{cachr}}:] { \footnotesize A tool for effective caching in CI/CD; Based on sha of bunch of input folders, this'll cache selective output folders to S3; Sha ensures caching happens only incase of changes in input folder }
\end{description}

\end{document}


%%%%%%%%%%%%%%%%%%%%%%
% Would have completed this if I had not had all projects listed under "Skills".  
% Still a good idea.  See if I can fit it in somewhere...  Otherwise, just print it out and bring it to an interview if needed.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{Hardware Engineering Projects} % If printed as a seperate page, get more detailed in the descriptions!  What type of processor?  What program used? Etc.
	
	\begin{description}
		\item[4 and 8 bit RISC CPUs] {\footnotesize Simple CPUs designed using CircuitMaker (no HDL) which contained ALUs, counters, registers, and 1K RAM all designed from scratch}
		\item[Simple Calculator] {\footnotesize Designed a simple calculator from the ground up using Xilinx ISE and Verilog HDL} % Get schematic block diagram for this one!
		\item[Stereo Amplifier] {\footnotesize Contained I/O as well as bass, treble, and volume controls}
		\item[Power Supply Basics] {\footnotesize Learned about the very basics of power supply design using transformers, rectifiers, and zener diodes and voltage regulators.} 
		\item[Parallel Port Game Controller] {\footnotesize Went through the start to finish development process of a game controller including driver development, microprocessor  \& ADC design (8255 MicroBoard; N.I.	ADC0809), and PCB design}
		\item[Portable Microphone Amplifier] {\footnotesize Utilized a series of transistors to amplify sound in a room with a potentiometer as volume control}
		\item[MP3 Player] {\footnotesize Developed an MP3 player using the Analog Devices BlackFin BF533 microprocessor and EZ-KIT development kit which utilized interrupts and audio codec}  % get link to block diagram for this one!
		\item[INL Remote Cell Phone Control] {\footnotesize Senior project which developed a prototype for Idaho National Laboratories allowing them to remote control a cell phone via 802.11g and bluetooth at a range greater than 6000ft consisting of 3 major components: central control, wireless medium, and embedded systems for chuckar box}
		\item[Inverted Pendulum] {\footnotesize Used sliding mode feedback control and inverted pendulum kit to keep metal rod standing vertially on a swingin arm}
		\item[FM Transmitter] {\footnotesize Built a simple FM Transmitter based off of given schematics as an introduction to FM modulation signals}
	\end{description}


\resheading{Software Engineering Projects}  % There really are a TON of projects I can put on this, but here are some major ones:
	\begin{description}
		\item[Book Keyword Scanner] {\footnotesize Developed a program which will take any input file and, given a keyword search, will return the frequency of that word }
		\item[Pedigree Chart] {\footnotesize Developed a program which will parse through a pedigree file and display a pedigree chart in the command line}
		\item[Factory Nail Rejection] {\footnotesize This program was simulating a factory which produced nails that had to be a very specific length, and if it wasn't, the program would reject it}
		\item[Calendar Program] {\footnotesize Given the time and date to display, the calendar program would display a simple calendar on the command line which took into account leap years}
		\item[Normal Distribution] {\footnotesize This program simulated the classic wheel of fortune blinko game where several thousand chip were statistially recorded and displayed as they dropped into a board filled with pegs}
		\item[RSA Encryption] {\footnotesize Developed an application which utilized the RSA encryption method to encrypt and decrypt messages}
	\end{description}

\end{document}

%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
	\begin{center}
		\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
			Toby Rummans & Eric Karl & Gordon Smith \\
			Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\ 
			\vspace{10pt} 
			Memolinkcorp & BYU-Idaho & BYU-Idaho \\ 
			[removed] & 525 South Center St. & 525 South Center St.  \\
			Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
			[removed] & (208) 496-3097 & (208) 496-2816 \\
		\end{tabular*}
	\end{center}
	
% \end{document}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED	OR OLD

		\item 
			\ressubheading{\href{http://www.rexburgmotorsports.com/}{Rexburg Motorsports}}{Rexburg, ID}{Computer Systems Administrator}{Aug. 2006 -- Oct. 2006}
				{ \footnotesize
				\begin{itemize}
	            			\resitem{Managed file and application servers running Windows 2003 Server}
	            			\resitem{Performed all levels of hardware and software systems support for 40 computers and 10 printers}
				\end{itemize}
				}

		\item 
			\ressubheading{Bresnan Communications}{Billings, MT}{Teir 1 Technical Support}{Jan. 2006 -- April 2006}
				{ \footnotesize
				\begin{itemize}
					\resitem{Provided Bresnan customers with technical support over the phone.}
					\resitem{Receieved training on resolving networking, cable TV, and VOIP issues.}
				\end{itemize}
				}

		\item 
			\ressubheading{Northwestern Energy}{Billings, MT}{Summer Gas/Electrical Engineer}{May 2004 -- April 2005}
				\begin{itemize}
					\resitem{Interned with full time Gas/Electrical Engineers.}
					\resitem{Documented, mapped, and marked city streetlights using MS Access, GTViewer, FRAMME, and CAD.}
				\end{itemize} 


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: 
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources: 
http://www.tvmier.com/Resume_Education.html


